smdi: An R package to perform structural missing data investigations on partially observed confounders in real-world databases

### 2023-07-19 manuscript/manuscript.qmd
call it a day

code-fold: false
eval: false
echo: true
number-sections: false

format: 
  docx:
    reference-doc: custom-reference-doc.docx
    fig-cap-location: top
    tbl-cap-location: top

@@

```{r setup}
#| label: setup
#| include: false
#| eval: true
library(magick)
library(cowplot)
library(here)
library(tidyverse)
library(readxl)
library(gt)

biblio <- bibtex::read.bib("references.bib")
```

@@

In our previous work [@weberpals2023] and for the purpose of the `smdi` R package, we categorize the implemented principled missing data investigations into three groups of diagnostics, which will be discussed in this section @tbl-overview

@@

```{r}
#| label: tbl-overview
#| tbl-cap: "table caption test"
#| eval: true
#| echo: false
tbl1 <- readxl::read_excel(
  path = here("tables", "tables_manual.xlsx"),
  sheet = "table1"
  ) %>% 
  group_by(Group, `Group Description`) %>% 
  gt() %>% 
  tab_header(
    title = "Overview of the main functions of the smdi package."
    ) %>%
  tab_caption(
    caption = "Overview of the main functions of the smdi package."
    ) %>%
  tab_style(
    cell_text(weight = "bold"),
    locations = cells_column_labels(columns = everything())
  ) %>% 
  # tab_footnote(
  #   footnote = "hotelling1931",
  #   locations = cells_body(
  #     columns = Function,
  #     rows = Function == "**smdi_hotelling()**"
  #     )
  #   ) %>% 
  fmt_markdown()

>>>>

code-fold: false
echo: true
number-sections: false

format: 
  docx:
    reference-doc: custom-reference-doc.docx
    fig-cap-location: top

@@

```{r setup}
#| label: setup
#| include: false
library(magick)
library(cowplot)
library(here)
library(tidyverse)
library(readxl)
library(gt)
library(captioner)

table_cap <- captioner(prefix = "Table")
```

@@

In our previous work [@weberpals2023] and for the purpose of the `smdi` R package, we categorized the implemented principled missing data investigations into three groups of diagnostics, which will be discussed in this section (Table 1).

@@

```{r}
#| label: tbl_overview
#| eval: true
#| echo: false

tbl1 <- readxl::read_excel(
  path = here("tables", "tables_manual.xlsx"),
  sheet = "table1"
  ) %>% 
  group_by(Group, `Group Description`) %>% 
  gt() %>% 
  tab_caption(caption = "tbl-overview") %>% 
  tab_header(
    title = "Overview of the main functions in smdi."
    ) %>%
  tab_style(
    cell_text(weight = "bold"),
    locations = cells_column_labels(columns = everything())
    ) %>% 
  fmt_markdown()
